Verifying Demonstrations

### 2018-02-27 paper/intro.tex
Fixes typo in refs

The assumptions might
become sufficiently realistic in the near future, though, with
smartphone penetration on the rise, increased digitalization and government-issued credentials
available in some countries already now (e.g., Estonia, Germany), and
distance-bounding chips\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
might not unrealistically be integrated in phones or smartcards in the
future, and even phones with off-the-shelf hardware running in
RFID-emulation mode have shown
promising results~\cite{dbonsmartphones}.

>>>>

The assumptions might
become sufficiently realistic in the near future, though, with
smartphone penetration on the rise, increased digitalization and government-issued credentials
available in some countries already now (e.g., Estonia, Germany), and
distance-bounding chips\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
might not unrealistically be integrated in phones or smartcards in the
future, and even phones with off-the-shelf hardware running in
RFID-emulation mode have shown
promising results~\cite{DBonSmartphones}.
